---
title: "Gun Control Chi Square"
author: "Claire Madden"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm claire and I'm updating this markdown file here.
I'm going to do some data science! 


```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")

```

I am asking the question: Is there a significant difference in recommended gun control action for male and female respondents (where the question is should guns be easier, harder or the same difficulty to get)?

knock knock... 

who's there?

apples

claire: data wrangling and counts

```{r}


get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)


rownames(get_guns) <- c("Female", "Male") # reassign row names from 1, 2 to be more informative Female and Male
  

```

spread function uses a key value pair - give column you want to spread out into multiple columns and tell it what values are associated with each output

when we run chi-square, we want data frame that only contains counts 



